|

### 2023-02-07 paper_comparison/paper_comparison/paper_comparison.Rmd
major update: use effect size instead of log(effect size) to fit model
the intercept is fixed by a constant log(0.05/0.95) to give 5% power when effect size = 0

  # Italic if reject
  mutate(across(r:s, ~ kableExtra::cell_spec(.x, italic = as.numeric(.x) < 0.05)))

@@

```{r}
# The glm model for RESET test
conv_poly_glmmod <- poly_conv_sim %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(x_dist, log_effect_size, RESET4_p_value) %>%
  filter(x_dist == "uniform") %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
glm(reject ~ log_effect_size, family = binomial(), data = .)
```

@@

For non-linearity patterns, the power curve of RESET test climbs aggressively from
`r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 0), type = "response")) * 100)`% to `r round(unname(predict(conv_poly_glmmod, newdata = data.frame(log_effect_size = 2), type = "response")) * 100)`% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect, showing that RESET test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residual plots.

@@

```{r}
# Get bootstrap samples
get_boot_sample <- function(dat, times = 100) {
  map_df(1:times, 
         ~slice_sample(dat, n = nrow(dat), replace = TRUE) %>%
           mutate(boot_id = .x))
}

# Get bootstrap CI
get_boot_conf <- function(dat, 
                          .x,
                          .y,
                          times = 100, 
                          upper_q = 0.975, 
                          lower_q = 0.025) {

  # Construct the model formula
  mod_formula <- substitute(.y ~ .x)

  # Get the x variable name
  x_chr <- as.character(substitute(.x))

  # Prepare a sequence of x values
  x_seq <- seq(min(dat[[x_chr]]), max(dat[[x_chr]]), by = 0.01)

  # Properly construct the new data frame for prediction
  newdata <- data.frame(.x = x_seq)
  newdata[[x_chr]] <- x_seq

  # Get the prediction for each bootstrap sample   
  dat_pred <- map_df(1:times, function(i) {

    # Get a bootstrap sample
    dat_i <- slice_sample(dat, n = nrow(dat), replace = TRUE) %>%
      mutate(boot_id = i)

    # Fit the model on the sample
    mod_i <- glm(mod_formula, family = binomial, data = dat_i)

    # Get the prediction
    newdata$.pred <- predict(mod_i, newdata = newdata, type = "response")

    # Return the prediction
    newdata
  })

  dat_pred <- dat_pred %>%
    group_by(.x) %>%
    summarise(upper = quantile(.pred, upper_q), 
              lower = quantile(.pred, lower_q))
  dat_pred[[x_chr]] <- dat_pred$.x
  dat_pred
}
```

@@

```{r}
# Analyse uniform polynomial data
p <- vi_survey %>%
  filter(!null_lineup, 
         !attention_check, 
         type == "polynomial", 
         x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(log_effect_size, reject) %>%
  ggplot() +

  # Group the data by effect and reject to draw points
  geom_point(data = ~.x %>% 
             group_by(log_effect_size, reject) %>% 
             summarise(num_response = factor(n())),
           aes(log_effect_size, reject, size = num_response), 
           alpha = 0.3)  +

  # Draw conventional test power curve
  geom_smooth(data = poly_conv_sim %>% 
                filter(x_dist == "uniform") %>%
                mutate(log_effect_size = log(effect_size)) %>%
                select(-RESET3_p_value, 
                       -(RESET5_p_value:RESET10_p_value), 
                       -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +

  # Draw bootstrap CI for visual test
  # geom_ribbon(data = ~get_boot_conf(.x,
  #                                   log_effect_size,
  #                                   reject,
  #                                   times = 1000),
  #             aes(x = log_effect_size, 
  #                 ymin = lower, 
  #                 ymax = upper),
  #             fill = rev(rcartocolor::carto_pal(4, "Vivid"))[4],
  #             alpha = 0.2) +

  stat_smooth(data = ~get_boot_sample(.x, times = 1000),
              geom = "line",
              aes(log_effect_size, 
                  reject, 
                  col = "Visual test", 
                  group = boot_id),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE,
              alpha = 0.01) +

  # Draw visual test power curve
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 1.5, but for the visual test it is around 3.5."}

@@

@@

```{r}
# Analyse uniform heteroskedasticity data
p <- vi_survey %>%
  filter(!null_lineup, 
         !attention_check, 
         x_dist == "uniform", 
         type == "heteroskedasticity") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  select(log_effect_size, reject) %>%
  ggplot() +

  # Group the data by effect and reject to draw points
  geom_point(data = ~.x %>% 
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = factor(n())),
             aes(log_effect_size, reject, size = num_response), 
             alpha = 0.3) +

  # Draw conventional test power curve
  geom_smooth(data = heter_conv_sim %>% 
                filter(x_dist == "uniform") %>%
                mutate(log_effect_size = log(effect_size)) %>%
                select(-RESET3_p_value, 
                       -(RESET5_p_value:RESET10_p_value), 
                       -F_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value:SW_p_value) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +

  # Draw bootstrap CI for visual test
  # geom_ribbon(data = ~get_boot_conf(.x,
  #                                   log_effect_size,
  #                                   reject,
  #                                   times = 1000),
  #             aes(x = log_effect_size, 
  #                 ymin = lower, 
  #                 ymax = upper),
  #             fill = rev(rcartocolor::carto_pal(4, "Vivid"))[4],
  #             alpha = 0.2) +

  stat_smooth(data = ~get_boot_sample(.x, times = 1000),
              geom = "line",
              aes(log_effect_size, 
                  reject, 
                  col = "Visual test", 
                  group = boot_id),
              method = "glm",
              method.args = list(family = binomial),
              se = FALSE,
              alpha = 0.01) +

  # Draw visual test power curve
  geom_smooth(aes(log_effect_size, reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +

  # Theme
  theme_light(base_size = 5) +
  theme(panel.grid.major.x =  element_line(colour = "grey70", linewidth = 0.5)) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  scale_x_continuous(breaks = seq(0, 5, 0.5), minor_breaks = NULL) +
  scale_size_manual(values = c(1, 2, 3)) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", size = "# lineups")
```

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 1.5, but for the visual test it is around 3."}

@@

# Dataset for p-value comparison
p_value_cmp_dat <- vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(conv_reject = ifelse(conventional_p_value < 0.05, "Reject", "Not"),
         reject = ifelse(p_value < 0.05, "Reject", "Not")) %>%
  mutate(conv_reject = factor(conv_reject, levels = c("Reject", "Not")),
         reject = factor(reject, levels = c("Reject", "Not"))) %>%
  select(type, conv_reject, reject)

@@

dat_poly_j <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  select(shape, log_effect_size, reject, conv_or_not)

dat_poly_j %>%
  mutate(es_min = min(log_effect_size), 
         es_max = max(log_effect_size)) %>%
  nest(data = c(log_effect_size, reject)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ log_effect_size, 
                        family = binomial(), 
                        data = .x))) %>%
  mutate(reject = map(mod, function(mod) {
    result <- data.frame(log_effect_size = seq(es_min[1], es_max[1], 0.01))
    result$reject <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-es_min, -es_max, -data, -mod) %>%
  unnest(reject) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = shape), se = FALSE, span = 0.03) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "TealGrn")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

@@

dat_heter_a <- heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  select(a, log_effect_size, reject, conv_or_not)

# Manually fit the model
dat_heter_a %>%
  mutate(es_min = min(log_effect_size), 
         es_max = max(log_effect_size)) %>%
  nest(data = c(log_effect_size, reject)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ log_effect_size, 
                        family = binomial(), 
                        data = .x))) %>%
  mutate(reject = map(mod, function(mod) {
    result <- data.frame(log_effect_size = seq(es_min[1], es_max[1], 0.01))
    result$reject <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-es_min, -es_max, -data, -mod) %>%
  unnest(reject) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = a), se = FALSE, span = 0.03) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

```{r get-5-eval, cache = TRUE}
dat_uniform_5 <- map_df(1:1000, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = 5) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size, x_dist, type)) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(conv_or_not = "Visual") %>%
  select(-unique_lineup_id, -p_value, -effect_size)
```

```{r different-x-dist-poly-power, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 1000 times and the corresponding power curves are drawn with transparent grey lines. The vetical dotted line is drawn to indicate where the visual pattern start to become recognisable. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, the lognormal distribution produce lower power for both types of tests."}

@@

dat_x_dist <- list(
  poly_conv_sim %>% 
    mutate(log_effect_size = log(effect_size)) %>%
    select(x_dist, log_effect_size, RESET4_p_value) %>%
    rename(RESET_p_value = RESET4_p_value) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete",
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(reject = as.numeric(RESET_p_value < 0.05)) %>%
    mutate(conv_or_not = "Conventional") %>%
    mutate(type = "non-linearity") %>%
    select(type, x_dist, log_effect_size, reject, conv_or_not),

  heter_conv_sim %>% 
    mutate(log_effect_size = log(effect_size)) %>%
    select(x_dist, log_effect_size, BP_p_value) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete",
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
    mutate(conv_or_not = "Conventional") %>%
    mutate(type = "heteroskedasticity") %>%
    select(type, x_dist, log_effect_size, reject, conv_or_not),

>>>>

  # Italic if reject
  mutate(across(r:s, ~ kableExtra::cell_spec(.x, italic = as.numeric(.x) <= 0.05)))

@@

```{r cache = TRUE}
# Define the minimum and maximum effect size
min_poly_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "polynomial", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  min()
max_poly_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "polynomial", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  max()

# The glm model for RESET test
reset_poly_glmmod <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(x_dist, effect_size, log_effect_size, offset0, reject) %>%
  glm(reject ~ effect_size - 1, family = binomial(), data = ., offset = offset0)

# The prediction for all conventional tests on poly model
pred_conv_poly <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  select(-RESET3_p_value, -(RESET5_p_value:RESET10_p_value), -F_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value:SW_p_value) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))

# Data needed by the visual test
visual_poly_dat <- vi_survey %>%
  filter(!null_lineup, 
         !attention_check, 
         type == "polynomial", 
         x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(effect_size, offset0, reject)

# The glm model for visual test
visual_poly_glmmod <- glm(reject ~ effect_size - 1, 
                          family = binomial(), 
                          data = visual_poly_dat, 
                          offset = offset0)

# The prediction of the visual test
pred_visual_poly <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                               offset0 = log(0.05/0.95)) %>%
  mutate(power = predict(visual_poly_glmmod, 
                         type = "response",
                         newdata = data.frame(effect_size = effect_size,
                                              offset0 = offset0))) %>%
  mutate(log_effect_size = log(effect_size))

# The prediction of the boot visual test
pred_visual_poly_boot <- map_df(1:500, function(boot_id) {
  slice_sample(visual_poly_dat, n = nrow(visual_poly_dat), replace = TRUE) %>%
    nest(dat = c(effect_size, offset0, reject)) %>%
    mutate(mod = map(dat, 
                     ~glm(reject ~ effect_size - 1, 
                          family = binomial(), 
                          data = .x,
                          offset = offset0))) %>%
    mutate(power = map(mod, function(mod) {
      result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                           offset0 = log(0.05/0.95))
      result$power <- predict(mod, type = "response", newdata = result)
      result
    })) %>%
    select(-dat, -mod) %>%
    unnest(power) %>%
    mutate(log_effect_size = log(effect_size)) %>%
    mutate(boot_id = boot_id)
  })
```

@@

For non-linearity patterns, the power curve of RESET test climbs aggressively from
`r round(unname(predict(reset_poly_glmmod, newdata = data.frame(effect_size = exp(0), offset0 = log(0.05/0.95)), type = "response")) * 100)`% to `r round(unname(predict(reset_poly_glmmod, newdata = data.frame(effect_size = exp(2), offset0 = log(0.05/0.95)), type = "response")) * 100)`% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect, showing that RESET test is way more sensitive to the type of model defects that being considered. Meanwhile, no noticeable visual features can be spotted from the example residual plots.

@@

```{r}
# Analyse uniform polynomial data
p <- ggplot() +

  # Group the data by effect and reject to draw points
  geom_point(data = visual_poly_dat %>%
               mutate(log_effect_size = log(effect_size)) %>%
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = factor(n())),
             aes(log_effect_size, reject, size = num_response), 
             alpha = 0.3) +

  # Draw conventional test power curve
  geom_line(data = pred_conv_poly,
            aes(log_effect_size, power, col = name),
            size = 1) +

  # Draw boot visual test curves
  geom_line(data = pred_visual_poly_boot,
            aes(log_effect_size, power, col = "Visual test", group = boot_id),
            size = 1,
            alpha = 0.01) +

  # Draw visual test power curve
  geom_line(data = pred_visual_poly,
            aes(log_effect_size, power, col = "Visual test"), 
            size = 1) +

@@

```{r polypower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for non-linear patterns (uniform fitted values only). Main plot shows the power curves estimated using logistic regression, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 500 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much non-linearity in the residuals? For the RESET test this is around log effect size 2.5, but for the visual test it is around 3.5."}

@@

```{r cache = TRUE}
# Define the minimum and maximum effect size
min_heter_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "heteroskedasticity", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  min()
max_heter_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "heteroskedasticity", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  max()

# The prediction for all conventional tests on heter model
pred_conv_heter <- heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  select(-RESET3_p_value, -(RESET5_p_value:RESET10_p_value), -F_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value:SW_p_value) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_heter_es, max_heter_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))

# Data needed by the visual test
visual_heter_dat <- vi_survey %>%
  filter(!null_lineup, 
         !attention_check, 
         type == "heteroskedasticity", 
         x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(effect_size, offset0, reject)

# The glm model for visual test
visual_heter_glmmod <- glm(reject ~ effect_size - 1, 
                           family = binomial(), 
                           data = visual_poly_dat, 
                           offset = offset0)

# The prediction of the visual test
pred_visual_heter <- data.frame(effect_size = seq(min_heter_es, max_heter_es, 0.1),
                                offset0 = log(0.05/0.95)) %>%
  mutate(power = predict(visual_heter_glmmod, 
                         type = "response",
                         newdata = data.frame(effect_size = effect_size,
                                              offset0 = offset0))) %>%
  mutate(log_effect_size = log(effect_size))

# The prediction of the boot visual test
pred_visual_heter_boot <- map_df(1:500, function(boot_id) {
  slice_sample(visual_heter_dat, n = nrow(visual_heter_dat), replace = TRUE) %>%
    nest(dat = c(effect_size, offset0, reject)) %>%
    mutate(mod = map(dat, 
                     ~glm(reject ~ effect_size - 1, 
                          family = binomial(), 
                          data = .x,
                          offset = offset0))) %>%
    mutate(power = map(mod, function(mod) {
      result <- data.frame(effect_size = seq(min_heter_es, max_heter_es, 0.1),
                           offset0 = log(0.05/0.95))
      result$power <- predict(mod, type = "response", newdata = result)
      result
    })) %>%
    select(-dat, -mod) %>%
    unnest(power) %>%
    mutate(log_effect_size = log(effect_size)) %>%
    mutate(boot_id = boot_id)
  })
```

```{r}
# Analyse uniform heteroskedasticity data
p <- ggplot() +

  # Group the data by effect and reject to draw points
  geom_point(data = visual_heter_dat %>%
               mutate(log_effect_size = log(effect_size)) %>%
               group_by(log_effect_size, reject) %>% 
               summarise(num_response = factor(n())),
             aes(log_effect_size, reject, size = num_response), 
             alpha = 0.3) +

  # Draw conventional test power curve
  geom_line(data = pred_conv_heter,
            aes(log_effect_size, power, col = name),
            size = 1) +

  # Draw boot visual test curves
  geom_line(data = pred_visual_heter_boot,
            aes(log_effect_size, power, col = "Visual test", group = boot_id),
            size = 1,
            alpha = 0.01) +

  # Draw visual test power curve
  geom_line(data = pred_visual_heter,
            aes(log_effect_size, power, col = "Visual test"), 
            size = 1) +

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating human evaluations of lineups. Surrounding lines of the visual test show the estimated power of 1000 bootstrap samples. Small row of plots shows typical residual plots corresponding to specific effect sizes, marked by dashed lines in main plot. Where would you draw the line of too much heteroskedasticity in the residuals? For the BP test this is around log effect size 2.5, but for the visual test it is around 3.5."}

@@

# Dataset for p-value comparison
p_value_cmp_dat <- vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(conv_reject = ifelse(conventional_p_value <= 0.05, "Reject", "Not"),
         reject = ifelse(p_value <= 0.05, "Reject", "Not")) %>%
  mutate(conv_reject = factor(conv_reject, levels = c("Reject", "Not")),
         reject = factor(reject, levels = c("Reject", "Not"))) %>%
  select(type, conv_reject, reject)

@@

dat_poly_j <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(reject = as.numeric(RESET4_p_value <= 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(shape, effect_size, offset0, reject, conv_or_not)

dat_poly_j %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = shape), size = 1) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "TealGrn")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

@@

dat_heter_a <- heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(reject = as.numeric(BP_p_value <= 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(a, effect_size, offset0, reject, conv_or_not)

# Manually fit the model
dat_heter_a %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_heter_es, max_heter_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = a), size = 1) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

```{r get-5-eval, cache = TRUE}
dat_uniform_5 <- map_df(1:500, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = 5) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size, x_dist, type)) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(conv_or_not = "Visual") %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value)
```

```{r different-x-dist-poly-power, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. For visual tests, all the power curves are estimated using five evaluations on each lineup. For lineups with uniform fitted value distribution, the five evaluations are randomly sampled from the total eleven evaluations. The sampling process has been repeated for 500 times and the corresponding power curves are drawn with transparent grey lines. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests."}

@@

dat_x_dist <- list(
  poly_conv_sim %>% 
    rename(RESET_p_value = RESET4_p_value) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete",
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(reject = as.numeric(RESET_p_value <= 0.05)) %>%
    mutate(conv_or_not = "Conventional") %>%
    mutate(type = "non-linearity") %>%
    mutate(offset0 = log(0.05/0.95)) %>%
    select(type, x_dist, effect_size, offset0, reject, conv_or_not),

  heter_conv_sim %>% 
    mutate(x_dist = ifelse(x_dist == "even_discrete",
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(reject = as.numeric(BP_p_value <= 0.05)) %>%
    mutate(conv_or_not = "Conventional") %>%
    mutate(type = "heteroskedasticity") %>%
    mutate(offset0 = log(0.05/0.95)) %>%
    select(type, x_dist, effect_size, offset0, reject, conv_or_not),

  vi_survey %>%
    filter(!null_lineup) %>%
    filter(!attention_check) %>%
    group_by(unique_lineup_id) %>%
    summarise(across(everything(), first)) %>%
    filter(x_dist != "uniform") %>%
    mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
    mutate(reject = as.numeric(p_value <= 0.05)) %>%
    mutate(x_dist = ifelse(x_dist == "even_discrete", 
                           "Discrete", 
                           stringr::str_to_title(x_dist))) %>%
    mutate(conv_or_not = "Visual") %>%
    mutate(offset0 = log(0.05/0.95)) %>%
    select(type, x_dist, effect_size, offset0, reject, conv_or_not)
) %>%
